\bf Forecast Reconciliation: A geometric view with new insights on bias correction.

### 2019-08-31 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
moved boxplot
added discussion of boxplots

	\subsection{Orthogonal projection}

@@

	\todo{Rob can you please read to make sure you are happy with this.}Note here that we rely here on the generalised Pythagorean Theorem (which involves an equality).  In contrast, \cite{WicEtAl2019} follow \cite{VanErven2015a} in stating their result in terms of the Generalised Pythagorean Inequality.  The proof of \cite{WicEtAl2019} requires an assumption about convexity so that the angle between the base forecast and coherent subspace must be greater than 90 degrees.  The proof we have provided here requires no such assumption, since this may not hold for an arbitrary $\bm{W}$.  As such the statement from \cite{WicEtAl2019} that {\em``MinT reconciled forecasts are at least as good as the incoherent forecasts''} should be qualified; this is only true with respect to a loss function that depends on ${\bm W}$.  If Euclidean distance (or mean squared error) is used, there will be cases where the MinT estimator does not improve upon base forecasts.

	{\bf Discuss results in Figure 4 here}

@@

Starting from a training window of $100$ observations, i.e., Jan-$1998$ to Apr-$2006$ we generate $h=1$ to $h=6$ steps-ahead forecasts. Using a rolling window we repeat the exercise one observation at a time until the end of the sample. This generates $140~1$-step-ahead, $139~2$-steps-ahead through to $135~6$-steps-ahead forecasts available for forecast evaluation.

@@

\clearpage
	\subsection{Transformations and bias adjustment}

>>>>

	\subsection{Orthogonal projection}\label{sec:orthogonal}

@@

	\todo{Rob can you please read to make sure you are happy with this.}Note here that we rely here on the generalised Pythagorean Theorem (which involves an equality).  In contrast, \cite{WicEtAl2019} follow \cite{VanErven2015a} in stating their result in terms of the Generalised Pythagorean Inequality.  The proof of \cite{WicEtAl2019} requires an assumption about convexity so that the angle between the base forecast and coherent subspace must be greater than 90 degrees.  The proof we have provided here requires no such assumption, since this may not hold for an arbitrary $\bm{W}$.  As such the statement from \cite{WicEtAl2019} that {\em``MinT reconciled forecasts are at least as good as the incoherent forecasts''} should be qualified; this is only true with respect to a loss function that depends on ${\bm W}$.  If Euclidean distance (or mean squared error) is used, there will be cases where the MinT estimator does not improve upon base forecasts.  This will be demonstrated using a real data set in the empirical study in section~\ref{sec:comparebase}.

@@

@@

\clearpage

    \subsection{Comparison to Base Forecasts}\label{sec:comparebase}

    To demonstrate the implications of Theorem~\ref{th:distred} we consider the improvement of different reconciliation methods over base forecasts.  For each series the ARIMA model minimising AICc is chosen using the \verb|auto.arima()| function in the \verb|forecast| package.  Using these fitted models, base forecasts are produced for $h=1$ to $6$-steps ahead for each series in the hierarchy.  This is first carried out with a training sample of $100$ observations, i.e., Jan-$1998$ to Apr-$2006$. The training window is then rolled forward one observation at a time until the end of the sample. This generates $140~1$-step-ahead, $139~2$-steps-ahead through to $135~6$-steps-ahead forecasts available for forecast evaluation.

    After obtaining the base forecasts these are reconciled using three different methods; OLS reconciliation, WLS reconciliation using variance scaling\todo{George please check} and MinT use a shrinkage estimator for ${\bm W}$.  Squared forecast errors are computed for each series and aggregated, i.e. we compute the loss function described in Section~\ref{sec:othogonal}.  We then compute the difference in this loss function between base forecasts and reconciled forecasts, where positive values indicat that reconciled forecasts are more accurate. The boxplots in Figure~\ref{fig:BaseVSRecon_Fc} summarise the distribution of this measure over each rolling window.  As the theory predicts, OLS reconciliation always leads to an improvement relative to base forecasts, the entire boxplot for OLS reconciliation is above zero.  This is not the case for WLS and MinT which for some windows perform worse than base forecasts.  The boxplots also demonstrate that OLS reconciliation is more stable than WLS and MinT reconciliation, a result not entirely unsurprising since the latter two methods require estimation of a ${\bm W}$ matrix which in practice is not trivial.  Nonetheless when averaging over the entire rolling window the MinT estimator performs best on average which is again precisely what the theorem proved in \cite{WicEtAl2019} would suggest.

	\subsection{Transformations and bias adjustment}
